Usage metrics

### 2021-03-03 analysis/usage.Rmd
Graph of coverage vs revdep vs nb of static evals

# if n_static < n_tracer, adjust n_tracer to n_static
# Probably due to higher-order functions taking some eval
cov_packages <- cov_packages %>%
  mutate(n_static = if_else(n_static < n_tracer, n_tracer, n_static))

cov_packages <- cov_packages %>% mutate(coverage = 100 * n_tracer / n_static)

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage)) + 
  labs(x = "coverage (%)")

@@

>>>>

# if n_static < n_tracer, adjust n_tracer to n_static
# Probably due to higher-order functions taking some eval
cov_packages <- cov_packages %>%
  mutate(n_static_c = if_else(n_static < n_tracer, n_tracer, n_static))

cov_packages <- cov_packages %>% mutate(coverage = 100 * n_tracer / n_static_c)

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage), binwidth=1) + 
  labs(x = "coverage (%)")

@@

What is the actual coverage vs the expected coverage?
```{r}
corpus_cov<- C_raw %>% select(package, size, revdeps)

corpus_cov<- corpus_cov %>% left_join(cov_packages, by = "package") %>%
  mutate(revdeps = replace_na(revdeps, 0))

corpus_cov %>% ggplot() +
  geom_point(aes(x = coverage, y = revdeps, size = size)) + 
  scale_y_log10() +
  scale_size_area() +
  labs(x = "coverage (%)", y = "Reverse dependencies")

ggsave(path(PLOT_DIR, "coverage_per_package_size.pdf"))
```

```{r}
corpus_cov %>% ggplot() +
  geom_point(aes(x = coverage, y = revdeps, size = n_static)) + 
  scale_y_log10() +
  scale_size_area() +
  labs(x = "coverage (%)", y = "Reverse dependencies", size = "Static call sites")

ggsave(path(PLOT_DIR, "coverage_per_package_static_call_sites.pdf"))
```
